Automating G\"odel's Ontological Proof of God's Existence with Higher-order Automated Theorem Provers

### 2014-05-25 Papers/2014-ECAI/ECAI-51.tex
Fix typo

Current works \cite{J23,B9} of the first author and Paulson illustrate that many
expressive logics, including quantified (multi-)modal logics, can be
embedded into the classical higher-order logic (\HOL), which can thus be seen
as an universal logic \cite{C36}. For this universal logic, efficient automated
theorem provers have been developed in recent years, and these systems
were now employed in our work.

>>>>

Current works \cite{J23,B9} of the first author and Paulson illustrate that many
expressive logics, including quantified (multi-)modal logics, can be
embedded into the classical higher-order logic (\HOL), which can thus be seen
as a universal logic \cite{C36}. For this universal logic, efficient automated
theorem provers have been developed in recent years, and these systems
were now employed in our work.
